---
title: "R Notebook"
output: html_notebook
---
```{r}
dataCredit <- Credit
head(dataCredit)
```

#SOAL STATISTIKA
Using R, compute the following tasks.

#1. Compute the mean and the median of Rating, Cards, and Age
```{r}
median(dataCredit$Rating)
```
```{r}
median(dataCredit$Cards)
```
```{r}
median(dataCredit$Age)
```

#2. Compute the mode of Gender, Student, and Married
```{r}
modeOf(dataCredit$Gender)
```
```{r}
modeOf(dataCredit$Student)
```
```{r}
modeOf(dataCredit$Married)
```

#3. Compute the sample 10, 37, and 91 percentiles of Education
```{r}
quantile(x= dataCredit$Education, probs = 0.1)
```
```{r}
quantile(x= dataCredit$Education, probs = 0.39)
```
```{r}
quantile(x= dataCredit$Education, probs = 0.91)
```

#4. Compute the quartiles of Balance and its corresponding boxplot
```{r}
quantile(x= dataCredit$Balance, probs = c(0.25, 0.50, 0.75))
```
```{r}
boxplot(dataCredit$Balance, horizontal = TRUE)
```

#5. Compute the correlation and the scatter plot between pairs of Limit and Rating, Age and Card, Income and Education
#Limit and Rating
```{r}
newData <- data.frame(limit = dataCredit$Limit, rating = dataCredit$Rating)
newData
```

```{r}
plot(newData$limit, newData$rating)
```
```{r}
cor(newData)
```
#Age and Card
```{r}
newData <- data.frame(age = dataCredit$Age, cards = dataCredit$Cards)
newData
```

```{r}
plot(newData$age, newData$cards)
```
```{r}
cor(newData)
```
#Income and Education
```{r}
newData <- data.frame(income = dataCredit$Income, education = dataCredit$Education)
newData
```

```{r}
plot(newData$income, newData$education)
```
```{r}
cor(newData)
```

#SOAL PROBABILITAS
kita melempar dadu sebanyak n = 10 kali dan x adalah banyaknya angka 2 setelah semua lemparan. probabilitas kemunculan angka 2 dalam satu kali lemparan adalah p = 1/2, berapakah probabilitas kita mendapatkan
x = 6 angka 2, dari n = 10 lemparan.

```{r}
dbinom(x = 6, size = 10, prob = 1/2)
```
X<=6
```{r}
pbinom(q=6,size = 10, prob = 1/2)
```
Percentile ke-75
```{r}
qbinom(p = 0.75, size = 10, prob = 1/3)
```
simulasi 50 binomial random variabel

```{r}
rbinom(n= 50, size = 10, prob = 1/2)
```






